TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-03-26 main.tex
MC.

Here, we give an overview of \new{Tud datasets}. The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression. All datasets are provided in a common dataset format at \url{graphlearning.io}, and easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.

@@

The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}.

\section{Installation, baseline, and evaluation tools}

The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.

@@

@@

Our intention here is to investigate the benefits XXXX. More precisely, we address the following questions:
\begin{description}
	\item[Q1] dfgkposdk
	\item[Q2] dfdsfsdd
	\item[Q3] sdfsdfsdfsdfdssdf
\end{description}

@@

Describe kernel, gnns used

\paragraph{Datasets.}

\paragraph{Graph kernels.}

\paragraph{GNNs.}

We used the evaluation procedute described in~\cref{eval}, describe used hyperparamter

\subsection{Results and discussion}

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

>>>>

Here, we give an overview of \textsc{Tud datasets}. The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression. All datasets are provided in a common dataset format at \url{graphlearning.io}, and easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.

@@

The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}. The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.

@@

Repeat ten times?

@@

Our intention here is to provide baseline experiments, and compare graph kernels and GNNs. More precisely, we address the following questions:
\begin{description}
	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
	\item[Q2] ?
	\item[Q3] ?
\end{description}

@@

We used the following datasets, graph kernels, and GNN baselines.

\paragraph{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
\textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the appendix for dataset statistics.

\paragraph{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016}, and $\delta$-$2$-LWL$^+$ kernel~\cite{Mor+2019b} included in the \textsc{TUD Dataset} package. The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set. For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}. The number of iterations of the \textsc{$1$-WL}, \textsc{WL-OA}, and the  $\delta$-$2$-LWL$^+$ were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}

\paragraph{GNNs.} We used the GNN architectures \textsc{GCN}~\cite{Kip+2017}, \textsc{Sage}~\cite{Ham+2017}, \textsc{Gin} and \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} as neural baselines. For all experiments, we used the global mean operator to obtain graph-level outputs. For each dataset, we optimize the number of hidden units from $
\{16, 32, 64, 128\}$, the number of layers from $ \{2, 3, 4, 5\}$ and the learning rate from $ \{0.0001, 0.001, 0.01 \}$ with respect to the validation set. The batch size was fixed to $128$.

For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies. All experiments can be fulled reprodcued from the scripts provided at \url{XXX}.

\subsection{Results and discussion}
See~\cref{t2l}.

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule
